\documentclass[a4paper,11pt]{article}
\usepackage[left=0.7in,right=0.7in,top=0.8in,bottom=0.8in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage[normalem]{ulem}
\usepackage[dvipsnames]{xcolor}
\usepackage{titlesec}
\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{noitemsep,topsep=2pt,leftmargin=*}
\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
\hypersetup{colorlinks=false,pdfborder={1 1 1},urlbordercolor={cyan}}

\begin{document}

%-------------------- HEADER --------------------
\begin{center}
    {\huge \textbf{Manjari Pandey}} \\[4pt]
    \href{tel:+918349811123}{+91 8349811123} \quad
    \href{mailto:se23ucse108@mahindrauniversity.edu.in}{se23ucse108@mahindrauniversity.edu.in} \quad
    \href{https://www.linkedin.com/in/manjari-pandey-a95ba92a8/}{linkedin.com/in/manjaripandey} \quad
    \href{https://github.com/manjaripandey}{github.com/manjaripandey}
\end{center}

%-------------------- EDUCATION --------------------
\section*{Education}
\textbf{Mahindra University, Hyderabad} \hfill Aug 2023 – Jun 2027 \\
B.Tech in Computer Science and Engineering \hfill CGPA: 8.38 (till 5\textsuperscript{th} sem)

\textit{Merit and Scholarships:} \\
Awarded a scholarship for being in \textbf{top 10\%} of the batch

\textit{Relevant Coursework:} \\
Data Structures \& Algorithms, DBMS, OS, OOP, AI, ML, Optimization Techniques for AI, Theory of Computation

%-------------------- SKILLS --------------------
\section*{Skills Summary}
\textbf{Languages:} C, C++, Python, Java, JavaScript \\
\textbf{Web/Frameworks:} React.js, Node.js, Express.js, Flask, Tailwind CSS, Material UI \\
\textbf{Auth \& Security:} JWT, OAuth, bcrypt.js, Google ReCAPTCHA \\
\textbf{Libraries:} NumPy, OpenCV, MoviePy \\
\textbf{Tools \& Practices:} Git, GitHub, REST APIs, Unit Testing (Jest, React Testing Library) \\
\textbf{Foundations:} Data Structures \& Algorithms, OOP, OS, DBMS

%-------------------- EXPERIENCE --------------------
\section*{Experience}

\textbf{Software Developer Intern – Arka Softwares} \hfill Jun 2025 – Aug 2025 \\
Jaipur, India (On-site)
\begin{itemize}
    \item Built responsive UIs with \textbf{React}, Context API/Redux, and integrated REST APIs using Axios.
    \item Enhanced performance via lazy loading, code-splitting, and added unit tests (Jest, RTL).
    \item Worked in an \textbf{Agile} team, contributing to collaborative development.
\end{itemize}


\textbf{Member – Placement Cell, Mahindra University} \hfill Aug 2024 – Present
\begin{itemize}
    \item Coordinated communication between students and recruiters during hiring seasons.
\end{itemize}

%-------------------- PROJECTS --------------------
\section*{Projects}

\textbf{\uline{C-Shell}} \hfill Systems Programming (C)
\begin{itemize}
    \item Developed a custom Linux shell in \textbf{C} with piping, redirection, background execution, and persistent history.
    \item Implemented robust job control and signal handling (SIGINT, SIGTSTP), including \texttt{activities}, \texttt{fg}, \texttt{bg}, and \texttt{ping}.
    \item Added built-ins (\texttt{hop}, \texttt{reveal}, \texttt{log}) and a modular parser using POSIX calls like \texttt{fork}, \texttt{execvp}, and \texttt{pipe}.
\end{itemize}

\textbf{\uline{Buy-Sell @ MU}} \hfill MERN Stack
\begin{itemize}
    \item Campus-exclusive buy/sell platform built with \textbf{React}, \textbf{Tailwind}, \textbf{Node/Express}, and \textbf{MongoDB}.
    \item Secured MU-email login with JWT auth, \textbf{bcrypt} hashing, OTP verification, and Google ReCAPTCHA.
    \item Implemented product search/filter, cart & checkout, order history, and an AI-powered chatbot.
\end{itemize}


\textbf{\uline{\href{https://github.com/manjaripandey/ChessEngine-.git}{Python-based Chess Engine}}} \hfill Python
\begin{itemize}
    \item Chess engine using \textbf{Negamax} with alpha-beta pruning and \textbf{NumPy} for board logic.
    \item Integrated UCI protocol for GUI support.
\end{itemize}

\end{document}